Copy number inference with InferCNV

### 2024-07-10 analyses/cell-type-ewings/template_notebooks/cnv-workflow/01-marker-genes.Rmd
don't load Rproj in notebooks
don't use find git root

```{r}
project_root <- here::here()
renv::load(project_root)

knitr::opts_chunk$set(
  dev = "jpeg"
)
```

@@

```{r base paths}
# The base path for the OpenScPCA repository, found by its (hidden) .git directory
repository_base <- rprojroot::find_root(rprojroot::is_git_root)

# The current data directory, found within the repository base directory
data_dir <- file.path(repository_base, "data", "current")
sample_dir <- file.path(data_dir, "SCPCP000015", params$sample_id)

# The path to this module
module_base <- file.path(repository_base, "analyses", "cell-type-ewings")
```

>>>>

```{r}
knitr::opts_chunk$set(
  dev = "jpeg"
)
```

@@

```{r base paths}
# The current data directory, found within the repository base directory
data_dir <- file.path("..", "..", "data", "current")
sample_dir <- file.path(data_dir, "SCPCP000015", params$sample_id)

# The path to this module
module_base <- file.path("analyses", "cell-type-ewings")
```

### 2024-07-10 analyses/cell-type-ewings/template_notebooks/cnv-workflow/04-infercnv.Rmd
don't use find git root

---
title: "Copy number inference with InferCNV"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
params:
  sample_id: SCPCS000490
  library_id: SCPCL000822
  marker_gene_classification: "tumor-normal-classifications.tsv"
  infercnv_dir: "infercnv"
  results_dir: "annotate_tumor_cells_output"
---

>>>>

---
title: "Copy number inference with InferCNV"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
params:
  sample_id: SCPCS000490
  library_id: SCPCL000822
  marker_gene_classification: "tumor-normal-classifications.tsv"
  infercnv_dir: "infercnv"
  results_dir: "cnv_annotation"
---
